%----------------------------------
% Chapter 3
%----------------------------------


\section{Introduction}
This activity defines the boundaries and scope of GreenGrid Energy’s Information Security Management System (ISMS), following the guidelines of ISO/IEC 27001 (Clause 4.3). It identifies all people, processes, and technologies affected by security requirements and details any relevant exclusions.

\section{Identify Organization Stakeholders}
\begin{itemize}
    \item \textbf{Internal Stakeholders:}
    \begin{itemize}
        \item \textit{Executive Leadership}: CEO, CFO, CTO, CISO, Legal \& Administration
        \item \textit{Engineering \& Grid Operations}: Manages power distribution, SCADA oversight
        \item \textit{R\&D}: Researches and pilots grid optimization and analytics
        \item \textit{Customer Services \& Billing}: Handles customer data, billing systems
        \item \textit{Supply Chain Management}: Oversees vendor contracts, hardware procurement
        \item \textit{Human Resources (HR)}: Manages employee data, access control, training
    \end{itemize}
    \item \textbf{External Stakeholders:}
    \begin{itemize}
        \item \textit{Customers}: Residential and enterprise energy clients
        \item \textit{Regulatory Bodies}: Energy sector regulators, data protection authorities
        \item \textit{Suppliers \& Partners}: Hardware/software vendors, cloud providers
        \item \textit{Local Communities \& Investors}: Impacted by or invested in energy operations
    \end{itemize}
\end{itemize}

\section{Describe IT (Shared) Infrastructure and Systems}
\begin{itemize}
    \item \textbf{SCADA Systems}: Monitors and controls grid operations (OT domain).
    \item \textbf{Cloud \& Edge Computing}: Hybrid AWS/Azure setup for data analytics and IoT.
    \item \textbf{Networking}:
        \begin{itemize}
            \item OT Network (real-time operational controls)
            \item IT Network (corporate, administrative, and business services)
        \end{itemize}
    \item \textbf{OT/IT Convergence}: Secure integration of grid operations with corporate systems.
    \item \textbf{Enterprise Tools}: Microsoft 365 for collaboration, SAP ERP for planning.
    \item \textbf{Security Infrastructure}: Palo Alto firewalls, IDS/IPS, MFA solutions, etc.
\end{itemize}

\section{Identify Relevant Business Processes and Data}
\begin{itemize}
    \item \textbf{Engineering \& Grid Operations}: Real-time monitoring, telemetry data, SCADA.
    \item \textbf{R\&D}: Proprietary research, predictive analytics, intellectual property.
    \item \textbf{Customer Services \& Billing}: Customer records, billing info, PII, payment data.
    \item \textbf{Supply Chain Management}: Vendor contracts, procurement data, delivery schedules.
    \item \textbf{Human Resources}: Employee data, payroll, performance records.
    \item \textbf{Legal \& Administration}: Regulatory compliance documentation, financial records.
\end{itemize}

\section{Define ISMS Boundaries}
\begin{itemize}
    \item \textbf{Physical Scope}:
    \begin{itemize}
        \item Headquarters, branch offices, and on-premises data centers.
        \item Critical SCADA sites and edge computing nodes under direct control of GreenGrid.
    \end{itemize}
    \item \textbf{Logical Scope}:
    \begin{itemize}
        \item All IT and OT networks where GreenGrid processes or stores business-critical data.
        \item Cloud-based systems (AWS/Azure) that handle sensitive or regulated information.
    \end{itemize}
    \item \textbf{Organizational Scope}:
    \begin{itemize}
        \item All departments contributing to or relying on secure information management.
        \item Third-party and vendor relationships that influence compliance or security posture.
    \end{itemize}
    \item \textbf{Exclusions (If Applicable)}:
    \begin{itemize}
        \item Legacy systems scheduled for decommissioning (if not critical).
        \item Certain external facilities or environments not under GreenGrid’s control.
    \end{itemize}
\end{itemize}

\section{Individual Tasks}
Each project member will investigate their assigned department in depth, clarifying:
\begin{itemize}
    \item \textbf{Department-Specific Infrastructure \& Systems:}
    \begin{itemize}
        \item Application servers, specialized tools, data flows unique to the department.
        \item Current security measures, compliance requirements, and known gaps.
    \end{itemize}
    \item \textbf{Departmental Business Processes \& Data:}
    \begin{itemize}
        \item Confidentiality, integrity, and availability needs for departmental information.
        \item Critical workflows (e.g., contract management, analytics model development, billing).
    \end{itemize}
\end{itemize}

\section{Deliverables}
\begin{itemize}
    \item \textbf{ISMS Scope Documentation:} A formal statement capturing included networks, sites, stakeholders, and assets in line with ISO 27001 Clause 4.3.
    \item \textbf{Updated Organizational Report:} Incorporate final ISMS scope, stakeholder analysis, and any refinements to the existing case study details.
\end{itemize}

\section{Conclusion}
Defining the ISMS scope ensures that GreenGrid Energy’s security efforts focus on the most critical assets and processes. This structured approach serves as a foundation for subsequent activities—such as risk assessment and control implementation—aiming to safeguard the company’s operational technologies, proprietary research, and customer data.

