\section{Overview of the Project Team}
To address the multifaceted security and operational needs of GreenGrid Energy, a specialized project team has been assembled. Each member is entrusted with the study and improvement of one key department, while collaborating on a unified approach to overall security management.

\section{Composition and Roles}

\subsection*{Inês Ribeiro \quad (Research \& Development)}
\begin{itemize}
    \item Investigates the R\&D department’s current processes, focusing on data protection for proprietary algorithms and innovative energy solutions.
    \item Evaluates secure environments for collaboration with Engineering \& Grid Operations during technology pilots.
    \item Ensures that intellectual property is safeguarded against industrial espionage and cyber threats.
\end{itemize}

\subsection*{Manuela Leite \quad (Supply Chain Management)}
\begin{itemize}
    \item Analyzes procurement workflows, vendor reliability, and component lifecycle management.
    \item Reviews supplier security standards, particularly regarding hardware used in critical infrastructure.
    \item Develops guidelines to mitigate risks associated with third-party relationships and external dependencies.
\end{itemize}

\subsection*{Eduardo Sousa \quad (Customer Services \& Billing)}
\begin{itemize}
    \item Examines the processes for customer onboarding, contract management, and billing systems.
    \item Establishes protocols for protecting personally identifiable information (PII) and financial data.
    \item Collaborates with Legal \& Administration to ensure strict compliance with data protection regulations and fraud prevention.
\end{itemize}
\section{Collective Responsibilities}
In addition to individual areas of focus, the team works jointly on the following departments and organizational aspects:
\begin{itemize}
    \item \textbf{Engineering \& Grid Operations}: Coordinates with the R\&D department to integrate new technologies safely, emphasizing OT/IT network security.
    \item \textbf{Human Resources}: Integrates role-based access control and security awareness training, ensuring employees understand evolving threats and best practices. [NÃO ESQUECER DE ADICIONAR A DIREÇÃO DE RECURSOS HUMANOS]
    \item \textbf{Legal \& Administration}: Aligns departmental operations with relevant legislation, oversees incident reporting processes, and manages compliance frameworks.
    \item \textbf{Overall Cybersecurity Strategy}: Proposes policies, incident response plans, and risk mitigation strategies that address cross-departmental challenges.
\end{itemize}

\section{Forward-Looking Objectives}
The assembled team aims to:
\begin{enumerate}
    \item Conduct a comprehensive risk assessment identifying critical assets, vulnerabilities, and potential impacts across all departments.
    \item Develop an information security management system (ISMS) aligned with international best practices (e.g., ISO 27001 or NIST CSF).
    \item Strengthen secure convergence of OT and IT networks, accounting for real-time operations and corporate data management.
    \item Promote a culture of security awareness and continuous improvement throughout the organization.
\end{enumerate}

\section{Concluding Remarks}
GreenGrid Energy’s innovation-driven environment and critical role in infrastructure place it at a heightened risk for cybersecurity threats. Through a structured evaluation of each department’s responsibilities and risks, the project team will formulate strategies to bolster security, ensure compliance, and maintain operational excellence. This approach underscores the importance of integrated governance and highlights the need for specialized attention to R\&D, supply chain, and customer service processes in the evolving energy sector.
